---
title: "R Notebook: Improving Construct Validity in Studies of Technology Transfer"
author: "Malcolm S. Townes"
date: '(`r format(Sys.time(), "%B %d, %Y")`)'
output: 
    github_document: default
    html_notebook: default
    always_allow_html: yes
---

## Introduction
This is an R Notebook for an investigation on improving construct validity in studies of technology transfer.

## Project Set Up
The following code chunk enables the R Notebook to integrate seemlessly with the project organization format. This is normally included in the R Notebook to simplify file calls and enable file portability but it has been causing an error. Per Dr. Christopher Prener of Saint Louis University, the error is generated because the `here::here()` function has not been tested with certain combinations of functions. To work around this problem, I've embedded the `here()` function where I enter a file path when necessary.

```{r setup-project}
knitr::opts_knit$set(root.dir = here::here())
```

## Load Dependencies
The following code chunk loads package dependencies required to perform the necessary tasks. Basic tasks include importing, reading, wrangling, and cleaning data; selecting a subset of the data; checking for unique observations, and analyzing missing data. 
```{r load-dependencies}
library(tidyverse) # loads the basic R packages
library(here) # enables file portability
library(readr) # functions for reading data
library(dplyr) # functions for data wrangling
library(janitor) # functions for data cleaning
library(naniar) # functions for analyzing missing data
library(ggplot2) # functions for data visualizations
```

## Load Raw Data
The following code chunk imports the raw data from the `XLS` file.
```{r import-data}
DataRaw <- read.table("DataRaw/NBERpatents1963to1999/apat63_99.txt", sep = ",", header = TRUE, fill = TRUE, dec = ".") # import raw data
```

## Subset Data
The following code chunk creates a subset of the data for the period 1990 through 1995.
```{r subset-data-90-95}
DataRaw %>%
  filter(GYEAR>=1990) %>%
  filter(GYEAR<=1995) -> DataSubset90to95 # subset data
DataSubset90to95 <- as_tibble(DataSubset90to95) # convert data frame to tibble
DataSubset90to95 %>%
  filter(CLAIMS>0) %>%
  filter(CRECEIVE>0) -> DataSubset90to95
set.seed(1972)
Sample90to95 <- sample(1:nrow(DataSubset90to95), size = 2000, replace = TRUE, prob = NULL)
```

## Inspect Data
The following code chunk evaluates the sample data.  It first checks for missing data for each variable.  It then checks for missing data for each variable in each observation.  Then it checks for duplicate observations with the `PATENT` variable to determine if that variable can be used as a unique identifier for each observation.  Finally, it checks for duplicate observations across all variables to ensure that each observation is unique.
```{r inspect-data-90-95}
miss_var_summary(Sample90to95, order = TRUE)
miss_case_summary(Sample90to95, order = TRUE)
get_dupes(Sample90to95, PATENT)
get_dupes(Sample90to95)
```

## Clean Data
I did not perform any additional cleaning of the sample data.
```{r view-data}
View(Sample90to95, "Cleaned Sample Data 1990 to 1995")
```

## Save Data
The following code chunk saves the cleaned data.
```{r save-data}
write.csv(Sample90to95, here("Data/DataClean/NBERpatents1963to1999/NBERPatCit90to95Sample.csv"), append = FALSE)
```

## Histograms
The following code chunk displays histograms for the variables to visually inspect for normal distribution of the data.
```{r histograms}
histogramCRECEIVE <- ggplot() +
  geom_histogram(Sample90to95, mapping = aes(CRECEIVE))
histogramCMADE <- ggplot() +
  geom_histogram(Sample90to95, mapping = aes(CMADE))
histogramCLAIMS <- ggplot() +
  geom_histogram(Sample90to95, mapping = aes(CLAIMS))
histogramORIGINAL <- ggplot() +
  geom_histogram(Sample90to95, mapping = aes(ORIGINAL))
histogramGENERAL <- ggplot() +
  geom_histogram(Sample90to95, mapping = aes(GENERAL))
histogramRATIOCIT <- ggplot() +
  geom_histogram(Sample90to95, mapping = aes(RATIOCIT))
```

## Scatter Plots
The following code chunk displays scatter plots with `CRECEIVE` as the dependent variable against each of the the primary independent variables of interest to visually inspect for linear relationships between the dependent variable and each of the independent variables.
```{r scatter-plots}
scatterCMADE <- ggplot() +
  geom_point(Sample90to95, mapping = aes(x = CMADE, y = CRECEIVE))
scatterCLAIMS <- ggplot() +
  geom_point(Sample90to95, mapping = aes(x = CLAIMS, y = CRECEIVE))
scatterORIGINAL <- ggplot() +
  geom_point(Sample90to95, mapping = aes(x = ORIGINAL, y = CRECEIVE))
scatterGENERAL <- ggplot() +
  geom_point(Sample90to95, mapping = aes(x = GENERAL, y = CRECEIVE))
scatterRATIOCIT <- ggplot() +
  geom_point(Sample90to95, mapping = aes(x = RATIOCIT, y = CRECEIVE))
```
